Dissertation Manuscript

### 2023-10-19 paper.qmd
fix md

  <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/manuscript.html.md">
  <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;md <small>(download)</small>
  </a>

>>>>

  <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/manuscript.md">
  <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;md <small>(download)</small>
  </a>
